Comparing Machine Learning algorithms for classifying cognitive states from fMRI data

### 2012-11-10 article/article.tex
boe

Principal Component Analysis (PCA). As feature extraction method, we applied PCA. Ideally, the input vectors of the PCA should be the standardized Talairach coordinates, because we are conducting between-subject classification. As this coordinate system appeared to be inaccurate for this dataset, we were forced to use the voxel indices. The problem is that indices of different subjects may not map well onto each other, due to differences in brain size and shape. As a result, the accuracy of the PCA may be reduced.

>>>>

Principal Component Analysis (PCA). As feature extraction method, we applied PCA. Ideally, the input vectors of the PCA should be the standardized Talairach coordinates, because we are conducting between-subject classification. As this coordinate system appeared to be inaccurate for this dataset, we were forced to use the voxel indices. The problem is that indices of different subjects may not map well onto each other, due to differences in brain size and shape. As a result, the accuracy of the PCA may be greatly reduced.

Temporal dimensionality reduction. As described in the introduction, the peak of the BOLD response is approximately 5 seconds after a stimulus is presented. This means that the first scans after a stimulus may not represent activity related to this stimulus and should not be used for classification. To examine which scans provide maximal class information, we plotted the average BOLD activity per scan for all trials of all subjects, given a trial type and ROI. As can be seen in Figure, scans 10 to 20 provide maximal information for the first stimulus, while scans 23 to 33 provide maximal information for the second stimulus. The other scans were excluded. As a comparison,
